\mytitle

### 2024-06-20 paper/paper.tex
finished proofreading

\usepackage{graphicx}
\usepackage{subcaption}

@@

To provide context, Switzerland, a neighboring country to Germany, has a punctuality rate of 90 percent for long-distance train \citep{SBB2024}. 
The reliability of Deutsche Bahn trains is so poor, that the Swiss Federal Office of Transport proposed to stop German trains from entering too deep into the country in order to prevent cascading delays on their own trains  caused by the DB trains \citep{Magill2023}.

@@

In order to spend this money purposefully, an in-depth analysis of the German railway system is needed in order to determine plausible causes for unreliability and train delay. 
Hence to this event I want to discover if Social Network Analysis is a fitting tool in order to find structural causes for train delay that can only be eliminated by targeted investments.

@@

The act of predicting train delay has received a lot of a from science over the years, with the primary objective of enhancing customer satisfaction by reducing the unpredictability of travel times. 
Train delay prediction can also assist in more accurately planning the utilization of the train network by train traffic control \citep{Spanninger2022}. 
Despite the fact that this paper does not focus on train delay prediction, determining factors for train delay represent a vital component in the production of precise prediction model.

\cite{Spanninger2022} reviewed and classified a variety of prediction models, into event-driven and data-driven approaches. 
Event-driven model incorporate train-events, such as departure, arrival and pass-through in order to mimic the railway operation dynamics. 
On the other hand data-driven approaches generate their predictions utilizing historic train movement data, most of the models therefore are machine learning models. 
In this paper also relies on historic delay data derived from arrival and departure times whereas it could be classified as a data-driven approach.

\cite{Cheng90} for example created a delay estimation system based on non linear equations. 
They specifically introduced train timetables as a part of their model instead of assuming that trains are uniformly distributed over time. 
this paper also utilizes timetable data in order to calculate the required delay data.

\cite{Murali2010} created a linear regression model to predict railroad delay. 
However instead of historic train data they generated their training data by using a simulation and later applied the resulting model to subsections of the Los Angeles train network. 
The main part of this paper is also employing linear regression, nevertheless here the aim is find important factors that determine train delays and would therefore assist in the improvement of such a linear regression model.

Another academic paper written by \cite{Hauck2020} makes use of the same linear regression model, however they used a dataset that was provided by the german railway service and is structured in similar fashion to the one that will be constructed as a part of this research. 
The dataset contains timestamps of the excepted events and the actual time of the event to calculate the delay out of the difference. This at first glance seems almost identical to want will be executed in this paper, however the mentioned research was again only interested in providing an accurate prediction system.

Research that aims to determine factors that cause train delay has been conducted by \cite{Dingler2010}. The goal of this paper was gain a better understanding for delay-causing factors. 
They obtained their data from a railway simulation software and observed the relationship of delay and factors such as train volume or train speed.

@@

The first challenge was to obtain historical delay data for German trains. This was complicated by the fact that, unlike many other rail services, Deutsche Bahn does not provide open access to this data \citep[p.~5]{Spanninger2022}. 
Instead, only delay data for the previous eight hours could be retrieved from the official API. 
In order to obtain an acceptable amount of data, regular queries would have to be made over a period of months. This was not possible due to the time constraints of this research. 
However, the necessary data could be found on the Website \href{https://www.zugfinder.net/en/start}{Zugfinder}. This service provides historical delay data for up to two years if a subscription is purchased. 
The delay data is taken from the public timetable of trains and should therefore be as accurate as the official data. However, it only collects data for long-distance trains, unlike the official API, which also provides information on regional trains. 
For the purpose of this research, however, the available data is sufficient as regional trains have a punctuality rate of over 90 percent compared to around 70 percent for long-distance trains \citep{DBPunctuality2024}. 
As the site does not provide an API by default, a web scraper was written to collect a reasonable amount of data. The resulting source code is available on my personal GitHub repository \citep{repo}.

In order to gather the requisite data, I initially retrieved a list of all German train stations from the official Deutsche Bahn API. 
I then proceeded to remove all stations that do not accommodate trains. Furthermore, I collected metadata, which can be seen in Fig. 1 (build table). 
This data will later be used to determine possible dependencies on various forms of delay. With this list I searched through every departure board on \href{https://www.zugfinder.net/en/start}{Zugfinder}, utilizing the Selenium library in Python, with the goal of finding possible trains to retrieve timetable data from. 
This list was then searched through every departure board on zugfinder.net, utilising the Selenium library in Python, with the goal of finding possible trains to retrieve timetable data from. 
All trains were then processed in order to remove trains that partly operate outside of Germany, as no sufficient metadata was available for the later analysis.

Subsequently, I compiled the timetable for each train of the previous two months. This data then was processed in order to calculate the delay rates of the trains utilizing the contained arrival and departure times at every given stop.

@@

The obtained data was then preprocessed by again checking for possible non german train stops inside of the timetables. This happens due to the fact, that train lines can serve as a replacement train on lines that also operate outside of Germany. Next the remaining data was used to calculate various metrics necessary for later inspection (Fig2.). Moreover canceled stops were also removed. 
The list of possible stations retrieved earlier also needed to be updated, all stops that are not a part of the processed train data. Finally the network consists of 305 train stations that function as nodes and 1389 directed edges. The edges were constructed from the available timetable data.

@@

\begin{table}[]
  \centering
  \begin{tabular}{lllll}
  \hline
                 & \textbf{Metropolitan} & \textbf{Interchange} & \textbf{Feeder} &  \\ \hline
  amount         & 18                                    & 202                          & 83                              &  \\
  share     & 6 percent                             & 67 percent                   & 27 percent                      &  \\
  average platforms     & 16                            & 6                   & 3                 &  \\
  average degree & 30.39                                 & 9.17                         & 4.54                            &  \\ \hline
  \end{tabular}
  \caption{Different nodes types, their share, average degree and platforms}
   \label{fig:network-overview}
\end{table}

@@

\begin{itemize}
  \item Metropolitan railway stations are located in larger cities and handle a substantial amount of train traffic. 
  Consequently, a high number of trains arrive and depart from these stations, resulting in a disproportionately high average degree.
  \item It can be observed that interchange stations are considerably smaller than other types of stations, as evidenced by the number of platforms. They account for over two-thirds of the network's nodes. The average degree of interchange stations is almost identical to the degree of the general graph and is considerably higher than what would be assumed in a train station network. This is due to the fact that the underlying dataset only consists of long-distance trains.
  \item Feeder stations are smaller stations situated in more rural areas. Their primary function is to facilitate the connection of passengers to larger railway stations, enabling them to embark on their desired long-distance trains. Nevertheless, it is evident that some long-distance trains include these stations in their schedules.
\end{itemize}

@@

The network in general is also notably sparse, as evidenced by the edge density of approximately 0.015. 
A dyad census yielded 44,800 unlinked nodes, 435 mutually connected nodes, and 518 asymmetric nodes. 
The aforementioned findings can be attributed to the nature of the dataset. The data utilized in this study originates from long-distance railways, necessitating the use of well-developed tracks to enable the trains to operate at high speeds. Given the higher maintenance requirements of these tracks, alternative routes are rarely provided.

\begin{figure}[h]
  \includegraphics[clip=true,width=\columnwidth]{../data/visualizations/degree_dist.png}
  \caption{The degree distribution of the network}
   \label{fig:network-deg-dist}
\end{figure}

\begin{figure}[h]
  \includegraphics[clip=true,width=\columnwidth]{../data/visualizations/powerlaw_fit.png}
  \caption{Power-law fit of the obtained degree distribution}
   \label{fig:network-powerlaw}
\end{figure}

Nevertheless, the maximum distance of the network is relatively short, with the shortest path from Berchtesgaden, which is in close proximity to the Austrian border in Bavaria, to Klanxbüll, situated in the vicinity of the Danish border, being only 24 edges in length. 
It can be concluded that the presence of a passing node does not necessarily indicate the necessity for a train switch, which implies that every destination in this network is quite reachable. The reciprocity is also quite high at approximately 0.627, which can be interpreted as follows: If one were to travel to a particular destination via a specific number of stations, it is likely that a similar route exists which would allow one to return to their original point of departure.

@@

The predicted variable $Y$ is also populated with different choices throughout the experiments. Initially, both values for stations and for connections are present in order to identify relevant factors on both of them. 
Furthermore, stations have values for both incoming and outgoing delay properties in order to detect possible reasons in more detail. Finally, two different kinds of delay metrics are employed: the average delay and the standard deviation. 
The average delay denotes the average delay of all trains in order to capture the general idea of delay. Conversely, the standard deviation should reflect the overall reliability of the delay, given that reliability is also a significant factor for travelers. 
For instance, if a train is consistently five minutes late, the timetable can be adjusted accordingly. However, if the train is on time on some days but experiences significant delays on others, this can significantly impact traveler comfort and potentially result in passengers missing connecting trains.

For computing metrics on the network, the Python library \href{https://networkx.org/}{NetworkX} was employed. The linear regression was executed using the R programming language, with the \href{https://cran.r-project.org/web/packages/olsrr/index.html}{Oslrr} Package used to facilitate the identification of suitable regression variables.

@@

As previously stated in Chapter \ref{sec:Research methodology}, the centrality of a train station or a connection may influence the delay. The simplest measure of this is the degree, which simply counts the adjacent nodes. Since the data provides directed edges, the degree is separated into in-degree and out-degree.

@@

The betweenness centrality incorporates information about the brokerage of a particular node and therefore the shortest path connecting two railway stations \citep[p.~35]{Linton}. This centrality measure will be the starting point of the next linear regression model. It is unfortunate that the average delay of a station based on the betweenness centrality generates worse results than the model with degree centrality. The application of betweenness centrality to the standard deviation again signals a positive relationship, with the model exhibiting a very low p-value. Conversely, the adjusted R² is somewhat lower this time. As betweenness centrality can also be calculated for edges, this model was also explored. Unfortunately, this model did not yield any new insights.

@@

Previous models have indicated that metropolitan stations experience higher delays due to their higher degrees and larger number of platforms. This study examines the type of station as a potential predictor variable. The model actually proves this hypothesis. In contrast to the positive correlation between Metropolitan stations and average delay, Feeder railway stations have a negative influence on delay. 
This observation is consistent with the results of previous models, since these stations in general have fewer platforms and a low degree, as illustrated in Table~\ref{fig:network-overview}.

@@

The operator \textit{Nahverkehrsgesellschaft-Baden-Württemberg-MBH} has the second lowest p-value and a negative correlation of -3 with the average delay. 
Given that the mean of the average delay across the entire dataset is approximately 5.975, it can be concluded that the operator is performing extremely well. 
In order to ascertain the potential reasons for this performance, the number of operated stations was initially examined, as a low number of operated stations may be more easily managed. 
However, the operator from Baden-Württemberg actually operates 47 stations, which is equal to the operator from Bavaria and the highest amount in the dataset. 
One might then hypothesise that this particular station operator does not manage any metropolitan stations, given that the previous observations indicated that metropolitan railway stations tend to result in higher average delays. 
However, this hypothesis is also found to be incorrect, as this operator manages 16.6 percent of all metropolitan stations. 
In order to identify a potential explanation for this exceptional punctuality, it is necessary to conduct a review of Chapter~\ref{sec:Introduction}. 
Baden-Württemberg is situated in close proximity to the Swiss border. As the Swiss railway operator does not permit delays, the German trains also potentially crossing over to Switzerland require a precise schedule. 
It is important to note that trains that traverse other countries than Germany have been excluded from the railway network. This is because the railway network is an interdependent structure, and therefore, delayed trains in the network of Baden-Württemberg would also exert influence on trains crossing the Swiss border.

The second most significant p-value belongs to the operator \textit{Verkehrsgesellschaft Mecklenburg-Vorpommern-MBH}, which exhibits a more pronounced negative correlation with delay. 
The estimated value is -6.5. Despite operating at 17 stations, this operator still ranks fifth in the network in terms of the number of stations it serves. 
Conversely, this operator does not manage any metropolitan stations, which may account for this performance. 
Furthermore, the federal state of Mecklenburg-Vorpommern has only one international border with Poland, in contrast to Baden-Württemberg, which has multiple international borders. 
This results in less international train traffic to be managed in Mecklenburg-Vorpommern. However, this result reinforces the hypothesis that metropolitan train stations in general have a positive effect on delay.

As previously indicated in Table~\ref{fig:network-overview}, the data relating to the control center of each railway station included in the study were also provided.
As with the regression model that employed the operator as a predictor variable, a model that utilized the control center as a predictor variable also yielded a noteworthy insight.
The resulting model yielded a single statistically significant p-value for the control center at the main station in Nuremberg, Bavaria.
This particular station exhibited a highly positive correlation with the average delay, with an estimated value of 5.710. 
One possible explanation for this result is the geographical distribution of the stations. 
As is evident from Figure~\ref{fig:nb-control}, the controlled railway station is distributed over a considerable distance.

@@

Consequently, it may be more challenging to coordinate traffic among these stations with precision. 
Moreover, a significant proportion of the managed stations are situated in the north of Bavaria, at the border with other federal states. 
The aforementioned regions are overseen by other control centers, which necessitates coordination among these control centers, thereby rendering this region more challenging to control.

@@

Given that the operator with a negative influence on delay did not have a significant number of stations to manage, it may be a potential solution to reduce the size of some operating region in order to mitigate the impact of delay.

@@

However, the accuracy of the results is limited by the amount of data used. Since only two months of timetable data was considered, it would be a possible idea for future research to include data of a larger timespan. 
It may also be helpful to consider external events, such as holidays, or particular circumstances, as the number of trains handled by a train station also indicated a slight positive relationship with average delay.

@@

In this paper in linear regression models have been used in order to determine possible reasons for train delay based on centrality measures and additional collected metadata about train stations.

@@

Nevertheless, the current results are beneficial in directing spending towards potential areas for improvement in order to enhance the overall network reliability, thereby making commuting by train a more attractive proposition.
\pagebreak
\listoffigures
\listoftables
\printbibliography

>>>>

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{makecell}
\renewcommand{\cellalign}{tl}

@@

To provide context, Switzerland, a neighboring country to Germany, has a punctuality rate of 90 percent for long-distance trains \citep{SBB2024}. 
The reliability of Deutsche Bahn trains is so poor, that the Swiss Federal Office of Transport proposed to stop German trains from entering too deep into the country, in order to prevent cascading delays on their own trains  caused by the DB trains \citep{Magill2023}.

@@

In order to spend this money purposefully, an in-depth analysis of the German railway system is needed in order to determine plausible causes for unreliability and train delay. 
Hence to this event I want to discover if Social Network Analysis is a fitting tool in order to find potential causes for train delay that can only be eliminated by targeted investments.

@@

The act of predicting train delay has received a lot of attention from science over the years, with the primary objective of enhancing customer satisfaction by reducing the unpredictability of travel times. 
Train delay prediction can also assist train traffic control in more accurately planning the utilization of the train network \citep[p.~1]{Spanninger2022}. 
Despite the fact that this paper does not focus on train delay prediction, determining factors for train delay represents a vital component in the production of precise prediction model.

\cite{Spanninger2022} reviewed and classified a variety of prediction models, into event-driven and data-driven approaches. 
Event-driven models incorporate train-events, such as departure, arrival and pass-through in order to mimic the railway operation dynamics. 
On the other hand data-driven approaches generate their predictions utilizing historic train movement data, most of the models therefore are machine learning models. 
This paper also relies on historic delay data derived from arrival and departure times whereas it could be classified as a data-driven approach.

\cite{Cheng90} for example created a delay estimation system based on a system of non linear equations. 
They specifically introduced train timetables as a part of their model instead of assuming that trains are uniformly distributed over time. 
This paper also utilizes timetable data in order to calculate the required delay data.

\cite{Murali2010} created a linear regression model to predict railroad delay. 
However instead of using historic train data, they generated their training data by using a simulation and later applied the resulting model to subsections of the Los Angeles train network. 
The main part of this paper is also employing linear regression, nevertheless here the aim is find important factors that determine train delays and would therefore assist in the improvement of such a linear regression model.

Different research conducted by \cite{Hauck2020} makes use of the same linear regression model, however they used a dataset that was provided by the german railway service and is structured in similar fashion to the one that will be constructed as a part of this research. 
The dataset contains timestamps of the excepted events and the actual time of the event to calculate the delay out of the difference. This at first glance seems almost identical to what will be executed in this paper, however the mentioned research was again only interested in providing an accurate prediction system.

Research that aims to determine factors that cause train delay has been created by \cite{Dingler2010}. The goal of this paper was to gain a better understanding for delay-causing factors. 
They obtained their data from a railway simulation software and observed the relationship of delay and factors such as train volume or train speed.

@@

The first challenge was to obtain historical delay data for German trains. This was complicated by the fact that, unlike many other rail services, Deutsche Bahn does not provide open access to this data \citep[p.~5]{Spanninger2022}. 
Instead, only delay data for the previous eight hours could be retrieved from the \href{https://developers.deutschebahn.com/db-api-marketplace/apis/frontpage}{official API}. 
In order to obtain an acceptable amount of data, regular queries would have to be executed over a period of months. This was not possible due to the time constraints of this research. 
However, the necessary data could be found on the website \href{https://www.zugfinder.net/en/start}{Zugfinder}. This service provides historical delay data for up to two years if a subscription is purchased. 
The delay data is taken from the public timetable of trains and should therefore be as accurate as the official data. However, it only collects data for long-distance trains, unlike the \href{https://developers.deutschebahn.com/db-api-marketplace/apis/frontpage}{official API}, which also provides information on regional trains. 
For the purpose of this research, however, the available data is sufficient as regional trains have a punctuality rate of over 90 percent compared to around 70 percent for long-distance trains \citep{DBPunctuality2024}. 
As the site does not provide an API by default, a web scraper was written to collect a reasonable amount of data. The resulting source code is available on my personal GitHub repository \citep{repo}.

\begin{table}[b]
  \centering
  \begin{tabular}{ll}
  \hline
  attribute      & description                                                                                      \\ \hline
  type           & station type dependent on their size                                                             \\
  platforms      & \makecell{number of platforms available for trains \\ to depart or arrive}                                     \\
  operator       & \makecell{transportation companies, mostly from federal states, \\ that operate a network of railway stations} \\
  control center & \makecell{railway station that coordinates the train traffic of \\ the particular station}                     \\ \hline
  \end{tabular}
  \caption{Collected metadata of nodes used for later analysis}
  \label{fig:network-metadata}
\end{table}

In order to gather the requisite data, I initially retrieved a list of all German train stations from the official Deutsche Bahn API. 
I then proceeded to remove all stations that do not accommodate trains. Furthermore, I collected metadata, which can be seen in Table~\ref{fig:network-metadata}. 
This data will later be used to determine possible dependencies on various forms of delay. With this list I searched through every departure board on \href{https://www.zugfinder.net/en/start}{Zugfinder}, utilizing the Selenium library in Python, with the goal of finding possible trains to retrieve timetable data from. 
All trains were then processed in order to remove trains that partly operate outside of Germany, as no sufficient metadata was available for the later analysis.

Subsequently, I compiled the timetable for each train between April and Mai 2024. This data then was processed in order to calculate the delay rates of the trains utilizing the contained arrival and departure times at every given stop.

@@

The obtained data was then preprocessed by again checking for possible non german train stops inside of the timetables. This happens due to the fact, that train lines can serve as a replacement train on lines that also operate outside of Germany. Next the remaining data was used to calculate various metrics necessary for later inspection, such as the average delay of a station and its standard deviation. Canceled stops were ignored in those calculations. 
The list of possible stations retrieved earlier also needed to be updated. Only the stops that are part of the processed train data were kept. Finally the network consists of 305 train stations that function as nodes and 1389 directed edges. The edges were constructed from the available timetable data of the train lines.

@@

\begin{table}[h]
  \centering
  \begin{tabular}{lllll}
  \hline
                 & \textbf{Metropolitan} & \textbf{Interchange} & \textbf{Feeder} &  \\ \hline
  amount         & 18                                    & 202                          & 83                              &  \\
  share     & 6 percent                             & 67 percent                   & 27 percent                      &  \\
  average platforms     & 16                            & 6                   & 3                 &  \\
  average degree & 30.39                                 & 9.17                         & 4.54                            &  \\ \hline
  \end{tabular}
  \caption{Different nodes types, their share, average degree and platforms}
   \label{fig:network-overview}
\end{table}

@@

\begin{itemize}
  \item Metropolitan railway stations are located in larger cities and handle a substantial amount of train traffic. 
  Consequently, a high number of trains arrive and depart from these stations, resulting in a disproportionately high average degree.
  \item It can be observed that interchange stations are considerably smaller than other types of stations, as evidenced by the number of platforms. They account for over two-thirds of the network's nodes. The average degree of interchange stations is almost identical to the degree of the general graph and is considerably higher than what would be assumed in a train station network. This is due to the fact that the underlying dataset only consists of long-distance trains.
  \item Feeder stations are smaller stations situated in more rural areas. Their primary function is to facilitate the connection of passengers to larger railway stations, enabling them to embark on their desired long-distance trains. Nevertheless, it is evident that some long-distance trains include these stations in their schedules as well.
\end{itemize}

@@

The network in general is also notably sparse, as evidenced by the edge density of approximately 0.015. 
A dyad census yielded 44,800 unlinked nodes, 435 mutually connected nodes, and 518 asymmetric nodes, which can be attributed to the nature of the dataset. Since the data utilized in this study originates from long-distance railways, it necessitates the use of well-developed tracks to enable the trains to operate at high speeds. Given the higher maintenance requirements of these tracks, alternative routes are rarely provided.

\begin{figure}[!h]
  \includegraphics[clip=true,width=\columnwidth]{../data/visualizations/degree_dist.png}
  \caption{The degree distribution of the network}
   \label{fig:network-deg-dist}
\end{figure}

\begin{figure}[!h]
  \includegraphics[clip=true,width=\columnwidth]{../data/visualizations/powerlaw_fit.png}
  \caption{Power-law fit of the obtained degree distribution}
   \label{fig:network-powerlaw}
\end{figure}

Nevertheless, the maximum distance of the network is relatively short, with the shortest path from Berchtesgaden, which is in close proximity to the Austrian border in Bavaria, to Klanxbüll, situated in the vicinity of the Danish border, being only 24 edges in length. 
It should be mentioned that passing a node does not necessarily indicate a train switch, which implies that every destination in this network is reachable quite easily. The reciprocity is also quite high at approximately 0.627, which can be interpreted as follows: If one were to travel to a particular destination via a specific number of stations, it is likely that a similar route exists which would allow one to return to their original point of departure.

@@

The predicted variable $Y$ is also populated with different choices throughout the experiments. Initially, delay values for stations as well as connections are present in order to identify relevant factors on both of them. 
Furthermore, stations have metrics for incoming and outgoing delay properties in order to detect possible reasons in more detail. Finally, two different kinds of delay metrics are employed: the average delay and the standard deviation. 
The average delay denotes the average delay of all trains at a point of the network in order to capture the general idea of delay. Conversely, the standard deviation should reflect the overall reliability of the delay, given that reliability is also a significant factor for travelers. 
For instance, if a train is consistently five minutes late, the timetable can be adjusted accordingly. However, if the train is on time on some days but experiences significant delays on others, this can harshly impact traveler comfort and potentially result in passengers missing connecting trains.

For computing metrics on the network, the Python library \href{https://networkx.org/}{NetworkX} was employed. The linear regression was executed using the R programming language, with the \href{https://cran.r-project.org/web/packages/olsrr/index.html}{Oslrr} Package to facilitate the identification of suitable regression variables.

@@

As previously stated in Chapter \ref{sec:Research methodology}, the centrality of a train station or a connection may influence the delay. The simplest measure of centrality is the degree, which simply counts the adjacent nodes. Since the data provides directed edges, the degree is separated into in-degree and out-degree.

@@

The betweenness centrality incorporates information about the brokerage of a particular node and therefore the shortest path connecting two railway stations \citep[p.~35]{Linton}. This centrality measure will be the starting point of the next linear regression model. It is unfortunate that the average delay of a station based on the betweenness centrality generates worse results than the model with degree centrality. The application of betweenness centrality to the standard deviation again signals a positive relationship, with the model exhibiting a very low p-value. Conversely, the adjusted R² is somewhat lower this time. As betweenness centrality can also be calculated for edges, this model was also explored. Unfortunately, this model did not yield any new insights, either.

@@

Previous models have indicated that Metropolitan stations experience higher delays due to their higher degrees and larger number of platforms. This study examines the type of station as a potential predictor variable. The model actually proves the given hypothesis. In contrast to the positive correlation between Metropolitan stations and average delay, Feeder railway stations have a negative influence on delay. 
This observation is consistent with the results of previous models, since these stations in general have fewer platforms and a low degree, as illustrated in Table~\ref{fig:network-overview}.

@@

The operator \textit{Nahverkehrsgesellschaft-Baden-Württemberg-MBH} has the second lowest p-value and a negative correlation of $-3$ with the average delay. 
Given that the mean of the average delay across the entire dataset is approximately $5.975$, it can be concluded that the operator is performing extremely well. 
In order to ascertain the potential reasons for this performance, the number of operated stations was initially examined, as a low number of operated stations may be more easily managed. 
However, the operator from Baden-Württemberg actually runs 47 stations, which is equal to the operator from Bavaria and the highest amount in the dataset. 
One might then hypothesise that this particular station operator does not manage any Metropolitan stations, given that the previous observations indicated that metropolitan railway stations tend to result in higher average delays. 
However, this hypothesis is also found to be incorrect, as this operator manages 16.6 percent of all metropolitan stations. 
In order to identify a potential explanation for this exceptional punctuality, it is necessary to conduct a review of Chapter~\ref{sec:Introduction}. 
Baden-Württemberg is situated in close proximity to the Swiss border. As the Swiss railway operator does not permit delays, the German trains also potentially crossing over to Switzerland require a precise schedule. 
It is important to note that trains that traverse other countries than Germany have been excluded from the railway network. Nevertheless the railway network is an interdependent structure and therefore delayed trains in the network of Baden-Württemberg would also exert influence on the trains crossing the Swiss border.

The second most significant p-value belongs to the operator \textit{Verkehrsgesellschaft Mecklenburg-Vorpommern-MBH}, which exhibits a more pronounced negative correlation with delay. 
The estimated value is $-6.5$. Despite operating at 17 stations, this operator still ranks fifth in the network in terms of the number of stations it serves. 
Conversely, this operator does not manage any Metropolitan stations, which may account for this performance. 
Furthermore, the federal state of Mecklenburg-Vorpommern has only one international border to Poland, in contrast to Baden-Württemberg, which has multiple international borders. 
This results in less international train traffic to be managed in Mecklenburg-Vorpommern. However, this result reinforces the hypothesis that metropolitan train stations in general have a positive effect on delay.

As previously indicated in Table~\ref{fig:network-metadata}, the data relating to the control center of each railway station included in the study were also provided.
As with the regression model that employed the operator as a predictor variable, a model that utilized the control center as a predictor variable also yielded a noteworthy insight.
The resulting model yielded a single statistically significant p-value for the control center at the main station in Nuremberg, Bavaria.
This particular station exhibited a highly positive correlation with the average delay, with an estimated value of 5.710. 
One possible explanation for this result is the geographical distribution of the stations. <
As is evident from Figure~\ref{fig:nb-control}, the controlled railway stations are distributed over a considerable distance.

@@

Consequently, it may be more challenging to coordinate traffic among these stations with precision. 
Moreover, a significant proportion of the managed stations are situated in the north of Bavaria, at the border with other federal states. 
The aforementioned regions are overseen by other control centers, which necessitates coordination among these control centers, thereby rendering the traffic in this region more challenging to control.

@@

Given that the operator with a negative influence on delay did not have a significant number of stations to manage, it may be a potential solution to reduce the size of some operating regions in order to mitigate the impact of delay.

@@

However, the accuracy of the results is limited by the amount of data used. Since only two months of timetable data was considered, it would be a possible idea for future research to include data of a larger timespan. 
It may also be helpful to consider external events, such as holidays, since these events cause a higher traveler volume. Especially as the number of trains handled by a train station also indicated a slight positive relationship with average delay.

@@

In this paper linear regression models have been used in order to determine possible reasons for train delay based on centrality measures and additional collected metadata about train stations.

@@

Nevertheless, the small amount of data also yielded some helpful results, which proves the effectiveness of this method. The current results are beneficial in directing spending towards potential areas for improvement in order to enhance the overall network reliability, thereby making commuting by train a more attractive proposition.
\pagebreak
\listoftables
\listoffigures
\printbibliography
